updated_workflow

### 2024-04-13 README.Rmd
fix

>>>>

```{r}

#Figuring out where the samples start
start_of_samples = names(final_data)[which(names(final_data) == "z")+1]

# Combining with design matrix
long = final_data %>% 
 tidyr::pivot_longer(start_of_samples:length(.),names_to = "sample") %>% 
 inner_join(design_matrix,by = "sample")

# What is the control group called?
control_group = "DMSO_T0"

# calculating log2 FC
control_data = long %>% 
  filter(group == control_group) %>% 
  group_by(Peptide) %>% 
  summarise(control_mean = mean(value,na.rm = TRUE))

reference_group = "DMSO_T240"

reference_data = long %>% 
  filter(group == reference_group) %>% 
  group_by(Peptide) %>% 
  summarise(reference_mean = mean(value,na.rm = TRUE))

log2fc = inner_join(control_data,reference_data,by = "Peptide") %>% 
 dplyr::mutate(comparison = paste0(control_group,"_",reference_group),
         log2fc = log2(reference_mean/control_mean)) %>% 
  dplyr::select(Peptide,comparison,log2fc)

# Doing T tests

stat = long %>% 
  filter(group %in% c(control_group,reference_group)) %>%
  group_by(Peptide) %>%
  rstatix::t_test(value ~ group) %>%
  rstatix::adjust_pvalue(method = "fdr") %>% 
  mutate(comparison = paste0(group1,"_",group2))

combined = inner_join(log2fc,stat,by = c("Peptide","comparison"))

```

```{r}

# Lets do anova to see if there are any differences among groups
stat = long %>% 
  group_by(Peptide) %>% 
  rstatix::anova_test(formula = value ~ group) %>% 
  rstatix::adjust_pvalue(method = "fdr")

sig = stat %>% 
  as.data.frame() %>% 
  dplyr::filter(p.adj < 0.05) %>% 
  dplyr::pull(Peptide)

p1 = long %>%
  mutate(peptide %in% stat)
  ggplot(aes())

```
